\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2019-07-31 paper/manuscript_psrmNote.tex
plastered the preprocessing section with 'proceed with caution' and 'use your own brain' warnings

\subsection{Preprocessing}
Preprocessing is an important part of text-as-data research and choices made therein can have significant effects on the outcomes of an analysis \citep{denny2018text}. The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable variance between websites. Some of it is substantively informative and some of it is completely irrelevant. As an example of the latter, names of city officials and citizen petitioners feature frequently in city documents. The same is true for streets, locations and not least of all, the city itself. Since individual names recur at a much higher rate within a city than across the entire corpus, this would cause a topic model to cluster its topics by city. Consequently we require a tool which detects the signal in the noise and does so consistently for a discordant set of sources.

@@

To this end, we turn to a common method in natural langauge processing---part-of-speech (POS) tagging and named entity recognition (NER). As names convey no substantive information, NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups, as well as works of art (e.g., statutes).} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (the modal category), verbs, and adjectives. Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name. Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works differently by taking grammar and surrounding words into account to identify the dictionary form of a word. } POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}. To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell}).  A final and crucial step is the removal of duplicate documents, which occur very frequently on websites. In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion. %The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars. For most days in most cities, these calendars tend to be empty, but nevertheless contain a template, which would lead to the creation of a document in our corpus. These short and repetitive -- but numerous -- texts would pose severe problems to a topic model. Our approach preserves the valuable information contained within these calendars when cities do make use of them, but removes them when they offer no substantive data.

>>>>

\subsection{Preprocessing}
Preprocessing is an important part of text-as-data research and choices made therein can have significant effects on the outcomes of an analysis \citep{denny2018text}. As such, our advice given in this section, more than in any other, is specific to the problem of extracting meaningful textual information from municipal government websites, with the end goal of its use in a bag-of-words-based model. The techniques we employ might also be of use in other types of applications, but by no means should this section be regarded as a general-purpose manual for preprocessing. The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable variance between websites. Some of it is substantively informative and some of it is completely irrelevant. As an example of the latter, names of city officials and citizen petitioners feature frequently in city documents. The same is true for streets, locations and not least of all, the city itself. Since individual names recur at a much higher rate within a city than across the entire corpus, this would cause a topic model to cluster its topics by city. Consequently we require a tool which detects the signal in the noise and does so consistently for a discordant set of sources.

@@

To this end, we turn to a common method in natural language processing---part-of-speech (POS) tagging and named entity recognition (NER). In our case, names are the source of substantively uninteresting heterogeneity between cities, so NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups, as well as works of art (e.g., statutes).} However, we caution here that for many other applications, where the names of political actors might be of interest, this step is not recommended. Furthermore, we select words on the basis of their POS-tags, retaining only nouns (the modal category), verbs, and adjectives.\footnote{For applications outside of bag-of-words models, where the grammatical structure remains of interest, users might also want to retain other parts of speech.} Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name. Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works differently by taking grammar and surrounding words into account to identify the dictionary form of a word. } POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}. To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell}).  A final and crucial step is the removal of duplicate documents, which occur very frequently on websites. In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion. %The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars. For most days in most cities, these calendars tend to be empty, but nevertheless contain a template, which would lead to the creation of a document in our corpus. These short and repetitive -- but numerous -- texts would pose severe problems to a topic model. Our approach preserves the valuable information contained within these calendars when cities do make use of them, but removes them when they offer no substantive data.
